\section{Summary}

Signals that appear to be pure noise may contain hidden signals regarding non-local consciousness.
These signals could be analyzed to ``instrument the soul''.
Follow-up work to be done includes:

\begin{itemize}
	\item Add features to the QTSA app to facilitate signal identification.
	\item Analyze existing experimental data to search for new signals.
	\item Develop new sensor technologies using quantum and spin effects.
\end{itemize}

The social impetus for such work is to repair the dysfunction introduced by
new technologies such as social media and pseudo-anonymous communications.
Instrumenting the soul would provide a new way of interacting that is completely open and honest.

QTDSP could be key to solving the wetiko disease epidemic that has plagued humanity for the
last several millenia. 

\subsection{Peace on Earth}

The motivation behind QTDSP is to solve the world's most vexing social problems by
using technology to decapitate the Medusa.
At the root of problems such as social injustice, political malfeasance,
the threat of fascism, financial corruption, totalitarianism,
endless war, the threat of nuclear war, and our inability to address climate change
is a form of psychic blindness called \emph{wetiko}.

\emph{Wetiko} is an Algonquin word (\emph{windigo} in Ojibwa, \emph{wintiko} in Powhatan)
for a cannibalistic spirit that is driven by greed, excess, and selfish consumption.
It is the ``disease caused by yellow metal''.

This contagious psycho-spiritual disease of the soul, a parasite of the mind, is currently
being acted out en masse on the world stage via a collective psychosis of titanic
proportions \cite{Levy}.

Wetiko works through the blind spots of the unconscious and the projective tendencies of
the mind so as to hypnotize us via our mind’s own creative power to shape reality.
It renders people oblivious to their own madness and compels them to act
against their own best interests.
This mind-virus only has power over us to the extent it is not seen, so the way to heal
it is to see how it operates, both out in the world and within our own mind.

Electronic devices that detect and display wetiko can lead to its annihilation.
The productive capacity of the leading device manufacturers could literally change
the world, in a holistic and divine way, almost overnight.

Besides the development of sensors, which looks promising given the state of quantum
computer technology, a mathematical model of time is needed to translate signals
into something digestible by AI and pattern matching algorithms.


